\documentclass[a4paper, 11pt]{article}
\usepackage[T1]{fontenc}    % enhance fonts
\usepackage[utf8]{inputenc} % special characters are usable now
\usepackage{microtype}      % provides smooth text appearance and auto hyphenation
\usepackage{parskip}        % remove auto indentation from paragraph beginnings, use \indent

\begin{document}
    %% Introduction
    \title{Hello There!}
    \author{Ali}
    \date{\today}
    \maketitle      % Let there be light

    \section{INTRO TO \LaTeX}

    Hello there!
    This line doesn't add up, and it has an indentation as a paragrph. \footnote{Don't you darling}

    %%%%%%%%%   SPECIAL CHARACTERS   %%%%%%%%%
    But this line does. Now let's have some special characters.

    Statement \# 1:
    50\% of \$100 makes \$50.
    More special symbols are \&,\_,\{\},[],\textbackslash.

    %%%%%%%%%   TEXT FORMATTING   %%%%%%%%%
    Time for formatting.
    This text is \emph{emphasized}.
    This one is \textit{italic}, and this one is \textbf{bold}.
    \textsl{Slanted} text, \textsc{small caps} is like this.
    Such commands can be \textit{\textbf{nested}}.
    \emph{See what happens when \emph{emphasized} text gets \emph{emphasized again}}. % Only applies to emph
    By the way, don't forget to follow \texttt{https://github.com}.
    This is a \textrm{roman} text.

    Font declarations are nice. \sffamily
    Sans serif font is used. \ttfamily
    Typewriter is used. \rmfamily
    Roman font family is used. \sffamily
    Continuing sans-serif font family.
    % command           declaration           meaning
    % \textrm{}         \rmfamily               roman
    % \textsf{}         \sffamily               sans-serif
    % \texttt{}         \ttfamily               typewriter
    % \textbf{}         \bffamily               bold-face
    % \textmd{}         \mdseries               medium
    % \textit{}         \itshape                italic
    % \textsl{}         \slshape                slanted
    % \textsc{}         \scshape                small caps
    % \textup{}         \upshape                upright
    % \textnormal{}     \normalfont             default
    % \emph{}           \em                     emphasized

    \noindent
    Now let's explore font sizes.

    \noindent\tiny We \scriptsize start \footnotesize from \small small, \normalsize then get normal, \large big, and \LARGE bigger, \huge huge, and \Huge gigantic!
    \normalsize

    %%%%%%%%%   COMMANDS AND FUNCTIONS   %%%%%%%%%
    \noindent Now let's see how we create new functions.
    % \newcommand{command}[arguments][optional]{definition}
    \newcommand{\US}{United States}
    \newcommand{\bi}[1]{\textbf{\textit{#1}}}   % giving arguments
    \newcommand{\bio}[2][\bfseries]{{#1#2}}     % more arguments, optional parameter

    Now we can use our new command:\US.

    Then there is that \bi{bold and italic thing we created}.
    This one normally uses \bio{bold text}; on demand, uses \bio[\itshape]{italic text}.

    %%%%%%%%%   PARAGRAPH BOXES   %%%%%%%%%
    Now we would like to create a narrow text column. % \parbox[alignment]{width}{text}
    Text line.  % \quad produces some space
    \quad \parbox[b]{3cm}{this paragraph box is aligned from bottom line.}
    \quad \parbox{3cm}{I love K-Pop, but I love \TeX\ more.}            % alignment: c: center
    \quad \parbox[t]{3cm}{this paragraph box is aligned from top line.} % this one better

    This now applies with variables too.
    \begin{minipage}[t]{3cm}
        This is some other way of having paragraph boxes.
    \end{minipage}
    \\
    \\
    \\
    %%%%%%%%%   SPACING: DOTS   %%%%%%%%%
    Abbreviations are important, as for Maynard J. Keenan.
    Here LaTeX understands that this is an abbreviation because a capital has a dot afterwards, so LaTeX puts less spacing for it. \\
    But sometimes LaTeX does not understand abbreviations, such as etc. so we use etc.\ for abbreviation and\@. For ending the sentence(optional). \\
    Here are three dots... Yet here are three dots with more spacing\ldots
    \\
    \\
    %%%%%%%%%   DISPAYING QUOTES   %%%%%%%%%
    I previously said ``I have the high ground''

    \noindent Then Will Ramos said:
    \begin{quote}
        After all I have done, I will disappear.
    \end{quote}
    These were the actual words that changed my mind.


\end{document}
