\documentclass[openany]{book}

\usepackage{index}
\makeindex
% use makeindex file.idx to generate the index database, then compile
\usepackage{hyperref}               % this package is best when loaded last
\hypersetup{pdfauthor={Ali Ucar},
  pdftitle={Why Learn LaTeX},
  pdfsubject={You Should Learn LaTeX Immediately},
  pdfkeywords={latex,learn}}
% for hyperref:
% \href{URL}{text} makes text to a hyperlink, which points to the URL address
% \url{URL} prints the URL and links it
% \nolinkurl{URL} prints the URL without linking it
% \hyperlink{name}{text} makes text to a hyperlink, which points to the target name

\begin{document}

    \tableofcontents

    \part{First Part}
    \index{First Part}
    \chapter*{Preface}
    \index{First Part!Preface}
    Some preface text here.
    \addcontentsline{toc}{chapter}{Preface}
    \chapter{First Main Chapter}
    \index{First Part!First Chapter}
    \section{First Section of the First Main Chapter}
    \index{First Part!First Chapter!First Section}
    This section starts and ends here.
    \section{Second Section of the First Main Chapter}
    \index{First Part!First Chapter!Second Section}
    Second section here, hello there.
    \subsection{First Subsection of the Second Section Where First Main Chapter Occurs}
    \index{First Part!First Chapter!Second Section!Subsection}
    Subsection related thingies in here.
    \subsubsection[A Deeper Subsection]{Subsection of the subsection where the donkey's pussy got wet.}
    \index{First Part!First Chapter!Second Section!Subsection!subsubsection}
    Donkey's pussy got wet hell yeah.
    \chapter{Second Main Chapter}
    \index{First Part!Second Chapter}
    Not a long chapter here.

    \part{Second Part}
    \index{Second Part}
    \chapter{Third Main Chapter}
    \index{Second Part!Third Chapter}
    Here we have the second part and the third main chapter.
    \appendix
    \index{Appendix}
    \cleardoublepage
    \addtocontents{toc}{\bigskip}
    \addcontentsline{toc}{part}{Appendix}
    \chapter{Chapter Glossary}
    \index{Appendix!Chapter Glossary}
    Glossary yeah.
    \chapter{Symbols}
    \index{Appendix!Chapter Symbols}
    Some symbols here.

    \clearpage

    \printindex

\end{document}
